%%%% resume.tex
%%%% Sun Apr 20 23:03:50 2003
%%%%
%%%% My resume. 

\documentclass{resume}
\newcommand{\B}{& $\bullet\,$} % unused but kept for reference
\name{Brian M. Moore}
\address{{\tt mooreb@mooreb.com} \hfill (408) 393-3124 (mobile)}
\begin{document}
\begin{resume}
\begin{Objective}
To continue my career in software engineering, focusing on work where precision and correctness are required. 
\end{Objective}

\begin{Profile}
Brian is a seasoned software professional with 25+ years of experience
in designing and implementing horizontally scalable systems in Silicon
Valley and beyond. Brian also has experience guiding and assisting
engineering teams accomplish goals, using techniques ranging from 1:1
mentoring to driving broad organizational initiatives.
\end{Profile}

\begin{Employment}
\begin{job}{Senior Director, Security Engineering}
           {Walgreen Co., remote}
           {October~2024--present}

Provide technical leadership in the redesign and reimplementation of
Walgreens' network edge: transition from a traditional VPN to Secure
Edge (SASE) Zero Trust Network Architecture (ZTNA). Evaluate offerings
from many vendors. Work cross-functionally to address many different
types of challenge: technical, political, financial, process, and
cultural.
           
\end{job}

\begin{job}{Distinguished Engineer, Infrastructure}
           {BILL, San Jose, CA}
           {Jan~2023--October~2024}

Take a leadership role in a group effort to migrate BILL
infrastructure from on-prem to AWS. Assist SRE and SAE groups during
incidents. Work to improve existing deployment infrastructure. Provide
inputs into both Disaster Recovery (DR) and Business Continuity
Processes (BCP). Lead application and infrastructure teams in the
migration of hundreds of terabytes of documents from NFS mounted
storage to S3. Mentor engineers with a focus on measurement, often
using the Socratic method.

\end{job}

\begin{job}{Principal Engineer}
           {Cirrus Software LLC, Santa Cruz, CA}
           {March~2016--present}

Help clients with software projects, including but not limited to design and implementation, cloud migration, DevOps, problem solving, and all other matters of software engineering.

\end{job}

\begin{job}{Application Development Principal}
           {PROUnlimited obo Cigna}
           {January 2021--May~2022}

Address long-standing technical debt by migrating mainframe VSAM legacy plan file data to DCRS.

\end{job}
\begin{job}{Distinguished Engineer, Vice President Technologies}
           {American Express Company, Enterprise Growth Division, New York, New York}
           {April~2014--February~2016}

Introduce cloud computing concepts to Serve: openstack, Asgard,
bakery. Introduced graphite to bring transparency to a previously
opaque operational model. Helped transform Amex's Foreign Exchange
platform from waterfall to an agile delivery model. Introduced a
microservice architecture by implementation of a configuration service
and guidance on REST resource modeling. Migrated 13 subversion
repositories, 90,000+ revisions, 8+ years of history into a single
subversion repository. Forwarded Amex's open-source contribution
model. Worked on BI/Big Data by getting Serve OLTP data into Hadoop
and writing Map/Reduce jobs.

\end{job}
\begin{job}{Senior Software Engineer}
           {Netflix, Inc., Los Gatos, California}
           {December~2010--April 2014}

Work as part of a team to transform Netflix's new user acquisition
from USA/English-only into an international effort: Canada, Latin
America, EU, Nordics, United Kingdom, Netherlands, and preparations
for other regions of the world. Reconstruct datacenter-based
infrastructure and back-end systems to take advantage of Amazon's Web
Services cloud-computing platforms (EC2, S3, etc.).  Design and
develop solutions to movie metadata distribution challenges.  Design
and implement ``Grapevine'', an event-based publishing system using S3
and Zookeeper to replace a simple but expensive polling
implementation. Grapevine was used to distribute metadata for the
first two years of Netflix Originals. Reduce average latency between
publication of movie metadata and consumption of that metadata from 30
minutes to sub-second.  Participate in the ``Cloud Performance:
Special Ops'' cross-functional working group. Implement and
open-source a Java Garbage Collection visualizer: gcviz.

\end{job}
\begin{job}{Principal Architect}
           {Yahoo!, Inc., Sunnyvale, California}
           {July~2008--December~2010}
Identify and resolve performance issues present in the Yahoo! Updates
platform, which publishes Yahoo!\ users' events across the
Yahoo!\ Network. Migrate the Yahoo!\ openness strategy (Y!OS) team
from CVS and Perforce to Subversion, moving 12+ years of history, 8+GB
of sources and 70,000+ revisions. Manage the MyBlogLog team through
its final founder leaving Yahoo! Design a store to securely hold (and
globally distribute) OAuth 1.0A, FB connect, OAuth 2.0, and other 3rd
party authorization tokens/credentials; co-lead a team through its
implementation. Develop processes to copy large data sets and use
Hadoop to analyze Yahoo! Address Book (\textasciitilde{}9TB) and the data
sources (\textasciitilde{}14TB) underlying the social features of Yahoo!
Contribute some of these technologies back to the Hadoop project.
\end{job}
\begin{job}{Senior Member of Technical Staff}
           {VMware, Inc., Palo Alto, California}
           {December~2007--July~2008}
Improve VMware engineers productivity by reducing build time, by
resolving long-standing build infrastructure issues, implementing
procedures to restore builds from tape, and developing build infrastructure.
\end{job}
\begin{job}{Senior Software Engineer}
           {Sputnik, Inc., San Francisco, California}
           {April~2007--December~2007}
Design and implement version 4.0 of the Sputnik Control Center,
a networking management system for wireless access points. Duties
include scaling and performance improvements.
\end{job}
\begin{job}{co-Founder, CIO}
           {Feder8.com, Inc., Sunnyvale, California}
           {January~2006--April~2007}
Co-founded Feder8.com, a computer-gaming community.
Responsibile for daily operations and development
of the server-side software and website.
\end{job}
\begin{job}{Computer Consultant}
           {Ultimate Technology Incorporated, San Jose, California}
           {December~2004--August~2006}
Assist Cisco Systems with the performance, scalability, resiliency,
and quality of its Wireless LAN Solution Engine (WLSE), WLSE
Express, and AON switch/routers in several hardware configurations.
\end{job}

\begin{job}{Founding Software Engineer}
           {Silver Spring Networks, San Mateo, California}
           {September~2003--October~2004}
Architect and implement a utility networking back-office system which communicates with up to 10,000 systems (``gateways'') each aggregating up to 1,000 gas, water, and electric meters.
\end{job}
\begin{job}{Computer Consultant}
           {Self-employed}
           {April~2002--September~2003}
Solve problems for clients. Two projects include processing of acoustic data received in a mining application and modeling the thickness of a pipe for a mining application.
\end{job}
\begin{job}{Senior Software Engineer}
           {NetVMG, Milpitas, California}
           {October~2001--April~2002}
Design, implement, and provide technical leadership in the 
management interface for a software/hardware route-control 
device for multi-homed hosts. Projects include building various 
methods for configuring and monitoring the device through SNMP 
while mentoring a team of younger engineers to do the same.
\end{job}

\begin{job}{Senior Software Engineer}
           {Epinions.com, Brisbane, California}
           {June~2000--October~2001}
Design and implement infrastructure to allow the website to function
correctly and efficiently. Projects include building a generic server
framework {\tt (http://mvserver.sourceforge.net/) } to instantiate
application servers which accept and perform requests, an event
distribution mechanism, a caching layer at the application level, and
implementation of the search functionality.
\end{job}

\begin{job}{Software Design Engineer}
           {Hewlett-Packard, Cupertino, California}
           {January~1999--June~2000}
Work as part of a team to modify the HotSpot Java Virtual Machine 
for PA-RISC/HP-UX 11.0. Projects include C++ name demangling 
for internal debugging and profiling support, a harness that 
generated tests for the internal assembler and disassembler, 
and thread and mutex debugging.
\end{job}

\begin{job}{Graduate Teaching/Research Assistant}
           {University of Kansas EECS department}
           {August~1996--December~1998}
  Grade projects for and assist in teaching EECS~665 Compiler Construction
  in the Spring~1996, Fall~1997, and Spring~1998 semesters.
  Research in the area of programming languages, including
  type-recovery, flow-analysis, and compiler construction.
  Research in the area of artificial intelligence, including
  machine-learning, theorem provers, and deductive-logic systems.
  Teach and grade two sections of EECS~188 Introduction to
  Programming in the Fall~1996 semester.
\end{job}

\begin{job}{Student Programmer/Consultant}
           {University of Kansas Computer Center}
           {May~1994--January~1997}
  Write and maintain data analysis and statistics code.
  Teach and supervise computer users.
  Engage in research and special projects.
\end{job}

\begin{job}{Customer Service Assistant}
           {University of Kansas Computer Center}
           {May~1992--May~1994}
  Provide microcomputer assistance to customers.
  Maintain print queues and more than forty microcomputers.
  Apply knowledge of many different software packages on several platforms. 
\end{job}
\end{Employment}

\begin{Projects}
  Several projects at {\tt https://github.com/mooreb/} \\*

  A Java Garbage Collection Visualizer \\*
    {\tt http://github.com/Netflix/gcviz } \\*
    {\tt http://techblog.netflix.com/2013/05/garbage-collection-visualization.html }

  A portable ANSI-C data structure and utility library: {\tt http://libmooreb.sourceforge.net/ }

  A generic server framework: {\tt http://arcs.sourceforge.net/ }

  A blackjack simulator: {\tt http://bjsim.sourceforge.net/ }

  A DEC-alpha Scheme compiler written in Scheme.

  A Java Virtual Machine written in Scheme.
\end{Projects}

\begin{Skills}
\begin{description}
\item[Programming Languages]  ANSI C, Python, Java, Perl, Scheme
\item[Operating Systems] UNIX, MacOS, MS Windows.
\end{description}
\end{Skills}

\begin{Education}
\begin{job}{University of Kansas}
           {Lawrence, Kansas}
           {August~1991--December~1998}
  MS, Computer Science with Honors. December~1998.

  BS, Mathematics. December~1995.
\end{job}
\end{Education}

\begin{Awards}
  National Merit Scholar.

  Kansas Scholar.

  Nerd For The New Millenium, Runner-Up.

  Eagle Scout. 
\end{Awards}

\begin{Activities}
  San Jose Tech Museum ``Tech Challenge'' judge, 2008--2012.
\end{Activities}

\begin{References}
References are available upon request.
\end{References}

\end{resume}
\end{document}
